---
title: "Lab 01"
author: "Matthew Kirchman"
date: "February 6, 2018"
output: 
  html_document:
    toc: TRUE
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("install.load")
install_load("mosaic")
install_load("ggplot2")
install_load("devtools")
install_load("tidyverse")


```

#Intro

This report is generated using data gathered on 970 unique Hollywood movies released between the years 2007 and 2013. It contains basic categorical information pertaining to the title, plot, and genre of each movie. It also contains integer values describing audience reviews of the movie and a wealth of information on how the movie performed financially, both during opening weekend and overall. The first few entries in this data set are provided below as examples:

```{r}
install_load("Lock5Data")


#I've spent 5 hours trying to do this lab, I clearly need to just move on because this isn't going to work how I want it to.
  #my_table = data.frame()
  #vector_length = 1:16
  #for (i in vector_length) { 
  #a = head(HollywoodMovies[i])
  #my_table = rbind(my_table, a)
  #}

head(HollywoodMovies)

#And now the head function works again. All I had to do was remove and re-add all of the variables in my global environment . . . I guess I must have accidentally messed with something earlier that caused it to get all screwed up.

#End result: 2 hours of my life entirely wasted on a problem that never existed to begin with.
```


#Summary of Data

Below are some summary statistics on three variables that are crucial to understanding the success of a Hollywood Movie. The first variable is "review_score", which I generated by averaging the  the critical rating that each movie received by professional reviewers on the popular review webstite "Rotten Tomatoes" with the score given to the movie by the audience at large on the same website. Both constituent scores, as well as the overall average score, are on a scale from 1 to 100.The second variable summarized here is "WorldGross", which detais the total gross revenue (in millions of U.S. Dollars) generated by each movie in box office sales around the world. Finally, the third variable summarized is "Budget", which is the production budget (in millions of U.S. Dollars) for each movie.
```{r}
#Average Review Score
review_score = (HollywoodMovies$RottenTomatoes + HollywoodMovies$AudienceScore)/2
summary(review_score)

#Gross Revenue (in millions $$$)
revenue_summary = summary(HollywoodMovies$WorldGross)
revenue_summary

#Total Production Budget (in millions $$$)
summary(HollywoodMovies$Budget)

```
 From these summaries, we can observe a few important things regarding the distribution of data. First, it appears that movie reviews scores are the most symmetrically distributed of the three variables, as the median score is nearly equal to the mean score. In contrast, the mean and median for Gross Revenue and Production Budget are both heavily skewed to the right, with means significantly higher than the median. This is most obvious in the case of revenue, where the mean value of `r revenue_summary["Mean"]`million is `r revenue_summary["Mean"]/revenue_summary["Median"]`of the median value of `r revenue_summary["Median"]` million. We can already tell that the Gross Revenue variable likely contains at least one outlier, as the maximum value of `r revenue_summary["Max."]` million is many clearly many standard deviations above the 3rd quartile value of `r revenue_summary["3rd Qu."]` million. This suggests that just a few really successful blockbuster movies are skewing the revenue distribution. 

# Production Budgets and Movie Success

But how do these variables relate to each other? Do movies with larger production budgets necessarily meet with greater success (audience reviews and gross revenue) than their low budget counterparts? The graphs below plot the relationship between the production budget of the 970 hollywood movies in our dataset and their success in terms of both audience reviews and total global revenue.

```{r}
plot (HollywoodMovies$Budget, review_score)
abline(lm(HollywoodMovies$Budget~review_score), col = "red")

plot(HollywoodMovies$Budget, HollywoodMovies$WorldGross)
abline(lm(HollywoodMovies$Budget ~ HollywoodMovies$WorldGross), col = "red")
```

These graphs reveal a positive relationship between movie production budget and critical and financial success. By superimposing a regression line (in red) over each scatterplot, we can see that the relationship between budget and critical reception is quite clearly positive. The relationship between budget and global revenue, however, is much less certain. The slope of the latter regression line is close to zero due to the seeming inability of budget to predict financial success at low values of budget; it appears likely that what slight positive slope we observe is directly attributable to the presence of a few highly influential outliers.

#Conclusion

Based on a simple analysis of summary statistics and scatterplots, it would appear that there is very likely a positive relationship between a movie's production budget and how well-recieved it is by critics. However, movie review scores appear to be much more evenly distributed than production budgets, so a linear model predicting review scores off of budget is certainly far from infallible. Even less clear is the relationship between the production budget and the gross revenue of a Hollywood movie, as a select few ultra-profitable movies appear to be skewing the data for the revenue variable.
